\documentclass{article}
%\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xintexpr}
\usepackage{multicol}
\usepackage{empheq}
\usepackage{forest}
\usepackage{booktabs}
\usepackage{ifthen}

\setlength{\columnsep}{0.5cm}
\setlength{\columnseprule}{1pt}

\newcommand{\T}{1}
\newcommand{\F}{0}
\newcommand{\TF}[1]{\if1#1\T\else\F\fi}
\newcommand{\xintTF}[1]{\xintifboolexpr{#1}{\T}{\F}}

\newcommand{\logicrule}[2]{
\begin{array}{l}
#1 \\
\midrule
\therefore #2 \\
\end{array}
}

\newcommand{\problem}[2]{$\boxed{\text{#1.#2}}$}
\newcommand{\subproblem}[3]{$\boxed{\text{(#3)}}$}
\newcommand{\solution}[3]{\boxed{#3\quad(\text{#1.#2})}}
\newcommand{\subsolution}[4]{\boxed{#4\quad(\text{#1.#2#3})}}

\newcommand{\inv}[1]{#1^{-1}}

\renewcommand{\d}[1]{\,\textnormal{d}#1}
\newcommand{\dd}[2]{\frac{\d{#1}}{\d{#2}}}
\newcommand{\ddd}[2]{\dfrac{\d{#1}}{\d{#2}}}

\setlength\parindent{0pt}
\setlength\parskip{0em}

\begin{document}

\section*{Homework 3}

%
\problem{2.1}{7}

Each event can be represented as a 2-tuple $(x,y)$, where $x$ is the
picture quality, and $y$ is the appearance quality. Each can take on
the values $x,y\in(D=\{p,g,s,f\})$, which stands for perfect, good,
satisfactory, and failed (respectively). Furthermore, we can determine
a score for each one: $C((x,y))$ for piCture quality, and $A((x,y))$
for appearance quality. These are defined as follows:

\[
C((x,y)):(D,D)\rightarrow\mathbb{R}
\] \[
C((x,y))=\begin{cases}4 & \text{if $x=p$} \\
2 & \text{if $x=g$} \\
1 & \text{if $x=s$} \\
0 & \text{if $x=f$}
\end{cases}
\]

and

\[
A((x,y)):(D,D)\rightarrow\mathbb{R}
\] \[
A((x,y))=\begin{cases}3 & \text{if $y=p$} \\
2 & \text{if $y=g$} \\
1 & \text{if $y=s$} \\
0 & \text{if $y=f$}
\end{cases}
\]

Finally, we can attach a total score to each event, $T(\sigma)$,
defined as:

\[
T(\sigma):(D,D)\rightarrow\mathbb{R}
\] \[
T(\sigma)=C(\sigma)\cdot A(\sigma)
\]

%
\subproblem{2.1}{7}{a} To construct the probability mass function, we
can create a table for all the event scores $(x,y)$, where the columns
are the $x$ values, and the rows are the $y$ values. Each entry is the
total score $T((x,y))$

\[
\begin{array}{c|cccc}
  & x=p & x=g & x=s & x=f \\
\midrule
y=p & 12 & 6 & 3 & 0 \\
y=g & 8 & 4 & 2 & 0 \\
y=s & 4 & 2 & 1 & 0 \\
y=f & 0 & 0 & 0 & 0 \\
\end{array}
\]

Then we can determine the range of the discrete random variable $T$,
which is:

\[
T(\sigma):(D,D)\rightarrow\{12,8,6,4,3,2,1,0\}
\]

Then we can construct the inverse image of the function as:

\[
\begin{array}{l|l}
e & \inv{T}\{e\} \\
\midrule
0 & \{(f,p),(f,g),(f,s),(p,f),(g,f),(s,f),(f,f)\} \\
1 & \{(s,s)\} \\
2 & \{(s,g),(g,s)\} \\
3 & \{(s,p)\} \\
4 & \{(g,g),(p,s)\} \\
6 & \{(g,p)\} \\
8 & \{(p,g)\} \\
12 & \{(p,p)\} \\
\end{array}
\]

And the PMF as:

\[
\subsolution{2.1}{7}{a}{\begin{array}{l|l}
e & P_T(e) \\
\midrule
0& 0.061 \\
1& 0.013 \\
2& 0.195 \\
3& 0.067 \\
4& 0.298 \\
6& 0.124 \\
8& 0.102 \\
12& 0.140 \\
\end{array}}
\]

%
\subproblem{2.1}{7}{b} We define the CDF, $F_T(e)$, as:

\[
F_T(e)=\sum\limits_{x\le e}P_T(e)
\]

Using this, we can construct the CDF as follows:

\[
\subsolution{2.1}{7}{b}{\begin{array}{l|l}
e & F_T(e) \\
\midrule
0& 0.061 \\
1& 0.074 \\
2& 0.269 \\
3& 0.336 \\
4& 0.634 \\
6& 0.758 \\
8& 0.860 \\
12& 1.000 \\
\end{array}}
\]

%
\subproblem{2.1}{7}{c} The outcomes are shipped can be summarized as:

\[
\beta=\{(s,g),(g,s),(s,p),(g,g),(p,s),(g,p),(p,g),(p,p)\}
\]

To find the most likely score, we can interpret that to mean the
weighted average score. In other words, we want to find the value of:

\[
\text{avg}=
\dfrac
    {\sum\limits_{\sigma\in\beta}T(\sigma)\cdot \dfrac{P(\sigma)}{\sum\limits_{x\in\beta}P(x)} }
    {(\max\{T(\sigma)|\sigma\in\beta\})-(\min\{T(\sigma)|\sigma\in\beta\})}
\]

Alternatively, we can look at it in terms of the PMF and CDF. If we
introduce $\Gamma=\{T(\omega)|\omega\in\beta\}$, then we have:

\[
\text{avg}=
\dfrac
    {\sum\limits_{e\in\Gamma}e\cdot \dfrac{P_f(e)}{\sum\limits_{x\in\Gamma}P_f(x)}}
    {|\Gamma|}
\]

It's important to note that the scores, $T(e)$, of each $e\in\beta$
falls in the range $\lbrack{}2,12\rbrack$. This means we can rely on
the CDF, by going back to the definition:



\[
F_f(x)=\sum\limits_{z\le x}P_f(z)
\] \[
\begin{array}{l}
F_f(12)-F_f(2)=\sum\limits_{z\le 12}P_f(z)-\sum\limits_{z\le 2}P_f(z) \\
F_f(12)-F_f(2)=\sum\limits_{2\le z\le 12}P_f(z) \\
\end{array}
\]

%
\problem{2.1}{9}

We are told the first value of the PMF, $P_X(1)$, is
$\frac{2}{5}$. Similarly, we can deduce that the value of $P_X(0)$ is
$0$, because there's no way we can pick the right warehouse if we
never call any of them.

We can construct a tree as follows, where the events to the left are
that the item is in the warehouse we call. We also introduce the
events $A_i$ for $i\in\{1,2,3,4\}$, which stand for the event that
call $i$ succeeds (but is not directly related to the event that call
$i-1$ succeeds or fails).

\begin{center}
\begin{forest}
  for tree={
    l sep=0.5cm,
    s sep=3cm,
    delay={
      edge label/.wrap value={node[midway,fill=white]{#1}}
    }
  }
  [$\circ$
    [$\dfrac{2}{5}$, edge label={$A_1$}]
    [$\dfrac{3}{5}$, edge label={$A_1'$}
      [$\dfrac{2}{4}$, edge label={$A_2$}]
      [$\dfrac{2}{4}$, edge label={$A_2'$}
        [$\dfrac{2}{3}$, edge label={$A_3$}]
        [$\dfrac{1}{3}$, edge label={$A_3'$}
          [$\dfrac{2}{2}$, edge label={$A_4$}]
          [$0$, edge label={$A_4'$}]
        ]
      ]
    ]
  ]
\end{forest}
\end{center}

We can then compute the probability of each event using the law of
total probability. The probability of the first one can be computed
trivially, as just the value of the left node from the top
(abbreviated as the path L).

\[
P_X(1)=P(A)
\] \[
P_X(1)=\frac{2}{5}
\]

The second one can be computed as intersection of the two
probabilities:

\[
P_X(2)=P(A_2A_1')
\]

%
\problem{2.1}{10}

Let $X$ be a random variable, which can take on any value in the
positive integers $\mathbb{Z}^+=\{1,2,\cdots\}$.

%
\subproblem{2.1}{10}{a} Suppose the PMF is defined, for some constant
$c$, as:

\[
P(X=i)=\frac{c}{i^2}
\] \[
P_X(i)=\frac{c}{i^2}
\]

We want to determine if this is a possible definition of the PMF. One
way to check is to look at the corresponding CDF:

\[
F_X(i)=\sum\limits_{z\le{}i}P_X(z)
\] \[
F_X(i)=\lbrack i\ge1\rbrack\sum\limits_{z=1}^i P_X(z)
\]

We know that the CDF should be $0$ for anything less than the minimum
value of the range of $i$. Suppose $k$ is an arbitrary integer less
than $1$. The value $F_X(k)$ can be found by:

\[
F_X(k)=\lbrack k\ge 1\rbrack\sum\limits_{z=1}^i P_X(z)
\]

Because we chose $k$ such that it is less than $1$, the Iverson
bracket at the beginning evaluates to $0$, so the CDF also evaluates
to $0$.

\[
F_X(k)=0
\]

We also know that the CDF should be $1$ on the other end of the range,
greater than the maximum of the range. Suppose we let $n$ be an
integer greater than $1$. The CDF for $n$ would be:

\[
F_X(n)=\lbrack n\ge 1\rbrack\sum\limits_{z=1}^n P_X(z)
\] \[
F_X(n)=\sum\limits_{z=1}^n P_X(z)
\]

By substituting the value for the PDF in question, we get:

\[
F_X(n)=\sum\limits_{z=1}^n\frac{c}{z^2}
\]

We can then take a limit to find the value of this sum as $n$ goes to
infinity:

\[
\lim\limits_{n\rightarrow\infty}F_X(n)=\lim\limits_{n\rightarrow\infty}\sum\limits_{z=1}^n\frac{c}{z^2}
\] \[
\lim\limits_{n\rightarrow\infty}F_X(n)=c\sum\limits_{z=1}^\infty\frac{1}{z^2}
\]

We know that the infinite sum of inverse squares converges, so if we
let $v$ equal that sum, then we have:

\[
\lim\limits_{n\rightarrow\infty}F_X(n)=cv
\]

If we chose $c=v^{-1}$, then this means that the CDF equals $1$ at
infinity, which means
$\subsolution{2.1}{10}{a}{\text{the PMF is valid}}$.

%
\subproblem{2.1}{10}{b} Now we want to look at the possibility of the
PDF being, for some constant c:

\[
P_X(i)=\frac{c}{i}
\]

By the same logic we used above, we will arrive at the infinite sum:

\[
\lim\limits_{n\rightarrow\infty}F_X(n)=c\sum\limits_{z=1}^\infty \frac{1}{i}
\]

However, we know that the infinite sum of inverse integers
diverges. Therefore, no matter what $c$ we choose, this sum will never
converge to $1$, so $\subsolution{2.1}{10}{b}{\text{this PMF is not valid}}$

%
\problem{2.1}{11}

Do we really just copy the handout..?

%
\problem{2.2}{6c}



%
\problem{2.2}{7b}

%
\problem{2.2}{8c}

%
\problem{2.2}{11}


\end{document}
